---
title: "GABM_Analysis"
author: "Kristiane Uhrenholt Warncke and Anne Skamris Holm"
date: "2024-11-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(readr)
library(ggplot2)
library(dplyr)
library(RColorBrewer)
```

```{r}
#Load data

data1 <- read.csv("~/Cognitive_Science/fifth_sem/BACHELOR/data/run_2024-11-28_21-03-55.csv")
data2  <- read.csv("~/Cognitive_Science/fifth_sem/BACHELOR/data/run_2024-11-29_17-06-35.csv")
data3 <- read.csv("~/Cognitive_Science/fifth_sem/BACHELOR/data/run_2024-11-29_19-48-52.csv")
data4 <- read.csv("~/Cognitive_Science/fifth_sem/BACHELOR/data/run_2024-12-01_15-51-34.csv")
data5 <- read.csv("~/Cognitive_Science/fifth_sem/BACHELOR/data/run_2024-12-02_08-06-05.csv")
data6 <- read.csv("~/Cognitive_Science/fifth_sem/BACHELOR/data/run_2024-12-05_11-27-40.csv")
data7 <- read.csv("~/Cognitive_Science/fifth_sem/BACHELOR/data/run_2024-12-05_16-00-43.csv")
data8 <- read.csv("~/Cognitive_Science/fifth_sem/BACHELOR/data/run_2024-12-06_12-10-04.csv")
data9 <- read.csv("~/Cognitive_Science/fifth_sem/BACHELOR/data/run_2024-12-07_15-52-23.csv")
data10 <- read.csv("~/Cognitive_Science/fifth_sem/BACHELOR/data/run_2024-12-08_07-48-48.csv")
data11 <- read.csv("~/Cognitive_Science/fifth_sem/BACHELOR/data/run_2024-12-08_21-03-01 copy.csv")
data12 <- read.csv("~/Cognitive_Science/fifth_sem/BACHELOR/data/run_2024-12-11_11-26-06.csv")
data13 <- read.csv("~/Cognitive_Science/fifth_sem/BACHELOR/data/run_2024-12-12_17-41-57.csv")

```

```{r}
# Combine all dataframes row-wise
data <- bind_rows(data1, data2, data3, data4, data5, data6, data7, data8, data9, data10, data11, data12, data13)
```


```{r}
#Expert ranking list

expert_ranking <- c(
  "A cosmetic mirror",
  "Overcoat (for everyone)",
  "2 litres of water per person",
  "Torch with 4 battery-cells",
  "Parachute (red & white)",
  "Folding knife",
  "Plastic raincoat (large size)",
  "45 calibre pistol (loaded)",
  "Sunglasses (for everyone)",
  "First-aid kit",
  "Magnetic compass",
  "Air map of the area",
  "A book entitled 'Desert Animals That Can Be Eaten'",
  "2 litres of 180 proof liquor",
  "Bottle of 1000 salt tablets"
)

# Add the expert ranking as a new column in the dataframe
data$expert_list <- rep(list(expert_ranking), nrow(data))

```

# CLEANING


```{r}
clean_column <- function(col) {
  # Step 1: Extract content within square brackets
  col <- gsub(".*\\[(.*)\\].*", "\\1", col)
  
  # Step 2: Remove leading ranking numbers (e.g., "1. ", "2. ")
  col <- gsub("\\s*\\d+\\.\\s*", "", col)
  
  # Step 3: Remove leading/trailing quotes (single or double quotes)
  col <- gsub("^['\"]|['\"]$", "", col)
  
  # Step 4: Convert strings into lists of items (split by commas)
  col <- lapply(col, function(x) {
    if (is.character(x) && length(x) > 0) {
      strsplit(x, ",\\s*")[[1]] # Split on commas and remove whitespace
    } else if (is.list(x)) {
      x # If already a list, return as is
    } else {
      NA # Replace invalid values with NA
    }
  })
  
  # Return the cleaned column
  return(col)
}

```


```{r}
#Combined function to clean spelling mistakes in items

fix_items <- function(lst) {
  sapply(lst, function(item) {
    # Define replacements as a named vector
    replacements <- c(
#Cosmetic mirror 
      "Cosmetic mirror" = "A cosmetic mirror",
      "COSMETIC MIRROR" = "A cosmetic mirror",
      "A COSMETIC MIRROR" = "A cosmetic mirror",
      
#Folding knife variations
      "FOLDING KNIFE" = "Folding knife",
      
#Raincoat variations
      "Plastic raincoat" = "Plastic raincoat (large size)",
      "Plastic raincoat (for sun protection)" = "Plastic raincoat (large size)",
      "PLASTIC RAINCOAT (LARGE SIZE)" = "Plastic raincoat (large size)",

#Salt tablets variations
      "1000 salt tablets" = "Bottle of 1000 salt tablets",
      "A bottle of 1000 salt tablets" = "Bottle of 1000 salt tablets",
      "Bottled 1000 salt tablets" = "Bottle of 1000 salt tablets",
      "Bottles of 1000 salt tablets" = "Bottle of 1000 salt tablets",
      "Salt tablets" = "Bottle of 1000 salt tablets",
      "BOTTLE OF 1000 SALT TABLETS" = "Bottle of 1000 salt tablets",

#Water variations
      "Two liters of water per person" = "2 litres of water per person",
      "Two litres of water per person" = "2 litres of water per person",
      "2 liters of water per person" = "2 litres of water per person",
      "Water" = "2 litres of water per person",
      "Canteen of 2 litres of water per person" = "2 litres of water per person",
      "Water (2 litres per person)" = "2 litres of water per person",
      "2 LITRES OF WATER PER PERSON" = "2 litres of water per person",

#Air map variations
      "Airt map of the area" = "Air map of the area",
      "A map of the area" = "Air map of the area",
      "AIR MAP OF THE AREA" = "Air map of the area",

#First aid-kit variations
      "A first-aid kit" = "First-aid kit",
      "FIRST-AID KIT" = "First-aid kit",

#Pistol variations
      "45 calibre pistol" = "45 calibre pistol (loaded)",
      "Pistol (loaded)" = "45 calibre pistol (loaded)",
      "45 caliber pistol (loaded)" = "45 calibre pistol (loaded)",
      "45 CALIBRE PISTOL (LOADED)" = "45 calibre pistol (loaded)",

#Overcoat variations
      "Overcoat" = "Overcoat (for everyone)",
      "OVERCOAT (FOR EVERYONE)" = "Overcoat (for everyone)",

#Parachute variations
      "Parachute" = "Parachute (red & white)",
      "A parachute (red & white)" = "Parachute (red & white)",
      "PARACHUTE (RED & WHITE)" = "Parachute (red & white)",

#Compass variations
      "Magnetic compass (for navigation)" = "Magnetic compass", 
      "MAGNETIC COMPASS" = "Magnetic compass",

#Liquor variations
      "2 liters of 180 proof liquor" = "2 litres of 180 proof liquor",
      "2 LITRES OF 180 PROOF LIQUOR" = "2 litres of 180 proof liquor",
      
#Sunglasses variations
      "Sunglasses for everyone" = "Sunglasses (for everyone)",
      "Sunglasses (for eye protection)" = "Sunglasses (for everyone)",
      "Sunglasses (for protection from the sun)" = "Sunglasses (for everyone)",
      "Sunglasses" = "Sunglasses (for everyone)",
      "Sun glasses (for everyone)" = "Sunglasses (for everyone)",
      "SUNGLASSES (FOR EVERYONE)" = "Sunglasses (for everyone)",
      
#Torch variations
      "Torches with 4 battery-cells" = "Torch with 4 battery-cells",
      "Torch with battery-cells" = "Torch with 4 battery-cells",
      "Torch with 4 battery cells" = "Torch with 4 battery-cells",
      "Torc with 4 battery-cells" = "Torch with 4 battery-cells",
      "torch with 4 battery-cells" = "Torch with 4 battery-cells",
      "TORCH WITH 4 BATTERY-CELLS" = "Torch with 4 battery-cells",

#Book variations
      "A book entitled 'Desert Animals That Can Be Eaten" = "A book entitled 'Desert Animals That Can Be Eaten'",
      "Book entitled 'Desert Animals That Can Be Eaten'" = "A book entitled 'Desert Animals That Can Be Eaten'",
      "Book on Desert Animals That Can Be Eaten" = "A book entitled 'Desert Animals That Can Be Eaten'",
      "Desert Animals That Can Be Eaten" = "A book entitled 'Desert Animals That Can Be Eaten'",
      "Book about desert animals that can be eaten" = "A book entitled 'Desert Animals That Can Be Eaten'",
      "A BOOK ENTITLED 'DESERT ANIMALS THAT CAN BE EATEN'" = "A book entitled 'Desert Animals That Can Be Eaten'"
    )
    
    
    # Replace the item if it matches a key in the replacements vector
    ifelse(item %in% names(replacements), replacements[item], item)
  }, simplify = TRUE, USE.NAMES = FALSE)
}

```


```{r}

## ONLY RUN CLEANING FUNCTIONS ONCE!!! ##

columns_to_clean <- c("group_list", "agent_1_list", "agent_2_list", "agent_3_list")

# Apply the cleaning function to each column 
data[columns_to_clean] <- lapply(data[columns_to_clean], clean_column)


# Apply the function to each column
data[columns_to_clean] <- lapply(data[columns_to_clean], function(col) {
  lapply(col, fix_items)
})

```


```{r}
# Count the number of rows for each personality trait
data_unfiltered <- data %>%
  count(personality)

# View the result
print(data_unfiltered)

```

```{r}
# Create dataframe for checking lengths of lists in each column
a <- data.frame(lapply(data[columns_to_clean], function(col) {
  sapply(col, length)
}))

# Rename columns
a <- a %>%
  rename(
    len_group_list = group_list,
    len_agent_1_list = agent_1_list,
    len_agent_2_list = agent_2_list,
    len_agent_3_list = agent_3_list
  )

# Add a index column to the data frames
a$index <- seq_len(nrow(a))
data$index <- seq_len(nrow(data))

#Merge data frames
data <- data %>%
  left_join(a, by = "index")
  
# Filter rows where all length columns have a value of 15
all_filtered_data <- data %>%
  filter(
    len_group_list == 15,
    len_agent_1_list == 15,
    len_agent_2_list == 15,
    len_agent_3_list == 15
  ) 

#Filter rows where one of the length columns are not 15
all_invalid_data <- data %>%
  filter(
    len_group_list != 15 | 
    len_agent_1_list != 15 | 
    len_agent_2_list != 15 | 
    len_agent_3_list != 15
  )

```

```{r}
## inspecting invalid data ##

#groups where agent_1 had an invalid list 
invalid_agent1_data <- data %>%
  filter(
    len_agent_1_list != 15
  )

#groups where agent_2 had an invalid list 
invalid_agent2_data <- data %>%
  filter(
    len_agent_2_list != 15
  )

#groups where agent_3 had an invalid list 
invalid_agent3_data <- data %>%
  filter(
    len_agent_3_list != 15
  )

#groups where group list was less than 15 but more than 0 
invalid_group_data <- data %>%
  filter(len_group_list > 0 & len_group_list != 15)

#groups that did not reach consensus within the turn-taking limit
no_consensus_data <- data %>%
  filter(
    len_group_list < 1
  )

#count zero length list-groups grouped by personality
no_consensus_count <- no_consensus_data %>%
group_by(personality) %>%
  summarize(count = n())

#count agent_1 flaws grouped by personality
invalid_agent1_count <- invalid_agent1_data %>%
group_by(personality) %>%
  summarize(count = n())

```


```{r}
# Remove "_1" from all items in the personality column
all_filtered_data$personality <- gsub("_1", "", all_filtered_data$personality)

```

# Thoughts
In order to convert the lists to the corresponding rank-numbers, we need to ensure that the items in the lists are written in the same way as the expert ranking. And if they are not, they need to be renamed. 


```{r}
#convert expert list and other lists to numeric values

# Create a named vector for mapping
rank_mapping <- setNames(seq_along(expert_ranking), expert_ranking)

# View the mapping
print(rank_mapping)

#function for mapping numbers to items
map_to_ranks <- function(list_column, rank_mapping) {
  lapply(list_column, function(row) {
    # Ensure row is a flat character vector
    unlisted_row <- unlist(row)  # Flatten the row
    # Map each item in the row to its corresponding rank
    as.numeric(rank_mapping[unlisted_row])
  })
}

#create a new column with expert numerical values 
all_filtered_data$expert_rank_num <- map_to_ranks(all_filtered_data$expert_list, rank_mapping)

# Map rankings to numeric values for agent_lists and group_list
### ONLY works if items are written exactly as in the expert_list ###

all_filtered_data$agent_1_rank <- map_to_ranks(all_filtered_data$agent_1_list, rank_mapping)
all_filtered_data$agent_2_rank <- map_to_ranks(all_filtered_data$agent_2_list, rank_mapping)
all_filtered_data$agent_3_rank <- map_to_ranks(all_filtered_data$agent_3_list, rank_mapping)
all_filtered_data$group_rank <- map_to_ranks(all_filtered_data$group_list, rank_mapping)

```

```{r}
# Add an index column to all_filtered_data
all_filtered_data$index <- seq_len(nrow(all_filtered_data))
```

```{r}
#checking for NA's in order to fix item names

# Columns to check
rank_columns <- c("agent_1_rank", "agent_2_rank", "agent_3_rank", "group_rank")

# Check for NAs in nested lists
sapply(rank_columns, function(col) {
  sum(sapply(all_filtered_data[[col]], function(x) any(is.na(x))))
})
```

```{r}
# Identify rows and columns with NAs
na_positions <- lapply(rank_columns, function(col) {
  which(sapply(all_filtered_data[[col]], function(x) any(is.na(x))))  # Get row indices with NAs
})

# Combine results into a named list for clarity
names(na_positions) <- rank_columns

# Print the list of positions
na_positions
```

```{r}
all_filtered_data$group_list[1249]
```

```{r}
# Exclude row 1249 from the dataset
all_filtered_data <- all_filtered_data[-1249, ]

#they chose to take an extra folding knife in the list instead of overcoats, which is not part of the rules for the task.
```


## CALCULATING TEAM SCORE AND SYNERGY SCORE

```{r}
#Function for calculating the Kendall tau correlation coefficient - as Team Score
# Compute Kendall's tau
calculate_kendall_tau <- function(expert_rank, agent_rank) {
  tau <- cor(expert_rank, agent_rank, method = "kendall")
  return(tau)
}
```


```{r}
# Calculate Kendall's tau for each agent and group
all_filtered_data$agent_1_score <- mapply(calculate_kendall_tau, all_filtered_data$expert_rank_num, all_filtered_data$agent_1_rank)
all_filtered_data$agent_2_score <- mapply(calculate_kendall_tau, all_filtered_data$expert_rank_num, all_filtered_data$agent_2_rank)
all_filtered_data$agent_3_score <- mapply(calculate_kendall_tau, all_filtered_data$expert_rank_num, all_filtered_data$agent_3_rank)
all_filtered_data$team_score <- mapply(calculate_kendall_tau, all_filtered_data$expert_rank_num, all_filtered_data$group_rank)
```


```{r}
# Calculating synergy score for each group 

# Calculate the mean of individual agent scores for each row
all_filtered_data$mean_agent_score <- rowMeans(all_filtered_data[, c("agent_1_score", "agent_2_score", "agent_3_score")], na.rm = TRUE)

# Calculate synergy score
all_filtered_data <- all_filtered_data %>%
  rowwise() %>%  # Process each row individually
  mutate(
    best_individual_score = max(c(agent_1_score, agent_2_score, agent_3_score), na.rm = TRUE),
    synergy_score = team_score - best_individual_score
  ) %>%
  ungroup()  # Ungroup after row-wise operation
```

```{r}
# Dataframe only with personality and scores 
score_data <- all_filtered_data %>%
  select(personality, agent_1_score, agent_2_score, agent_3_score, team_score, synergy_score) 

#round scores to 2 decimals
score_data <- score_data %>% 
  mutate(across(where(is.numeric), ~ round(., 2)))
```

```{r}
#Adding trait and level values
all_filtered_data <- all_filtered_data %>%
  mutate(
    Level = ifelse(grepl("^High", personality), "High", 
                   ifelse(grepl("^Low", personality), "Low", NA)),
    Trait = case_when(
      grepl("agree", personality, ignore.case = TRUE) ~ "Agreeableness",
      grepl("extra", personality, ignore.case = TRUE) ~ "Extraversion",
      grepl("neuro", personality, ignore.case = TRUE) ~ "Neuroticism",
      grepl("consc", personality, ignore.case = TRUE) ~ "Conscientiousness",
      grepl("open", personality, ignore.case = TRUE) ~ "Openness",
      TRUE ~ NA_character_  # Default case: assign NA if no match
    )
  )

# Reorder the Level column
all_filtered_data$Level <- factor(all_filtered_data$Level, levels = c("Low", "High"))
```


# SUMMARIZING

```{r}
# Summary statistics for each personality trait
summary_stats <- all_filtered_data %>%
  group_by(personality) %>%
  summarise(
    mean_team_score = mean(team_score),
    sd_team_score = sd(team_score),
    se_team_score = sd(team_score, na.rm = TRUE) / sqrt(n()),
    mean_synergy_score = mean(synergy_score),
    sd_synergy_score = sd(synergy_score),
    se_synergy_score = sd(synergy_score, na.rm = TRUE) / sqrt(n()),
    mean_turntakings = mean(turn_takings),
    sd_turntakings = sd(turn_takings),
    se_turntakings = sd(turn_takings, na.rm = TRUE) / sqrt(n()),
    group_count = n()  # Count of occurrences of each personality trait in groups
)

summary_stats <- summary_stats %>%
  mutate(
    Level = ifelse(grepl("^High", personality), "High", 
                   ifelse(grepl("^Low", personality), "Low", NA)),
    Trait = case_when(
      grepl("agree", personality, ignore.case = TRUE) ~ "Agreeableness",
      grepl("extra", personality, ignore.case = TRUE) ~ "Extraversion",
      grepl("neuro", personality, ignore.case = TRUE) ~ "Neuroticism",
      grepl("consc", personality, ignore.case = TRUE) ~ "Conscientiousness",
      grepl("open", personality, ignore.case = TRUE) ~ "Openness",
      TRUE ~ NA_character_  # Default case: assign NA if no match
    )
  )

# Reorder the Level column
summary_stats$Level <- factor(summary_stats$Level, levels = c("Low", "High"))

#Altering df for appendix plot
summary_stats_appendix <- summary_stats %>%
  rename(
    mean_team = mean_team_score,
    sd_team = sd_team_score,
    se_team = se_team_score,
    mean_synergy = mean_synergy_score,
    sd_synergy = sd_synergy_score,
    se_synergy = se_synergy_score
  )

#round values to 2 decimals
summary_stats_appendix <- summary_stats_appendix %>% 
  mutate(across(where(is.numeric), ~ round(., 2)))

mean_turntakings_all <- mean(all_filtered_data$turn_takings, na.rm = TRUE)
mean_turntakings_all
```


```{r}

all_filtered_data$Level <- factor(all_filtered_data$Level, levels = c("Low", "High"))

```

# VISUALIZING DATA

## Visualizing groups 

```{r}
ggplot(all_filtered_data, aes(x = Level, fill = Trait)) +
  geom_bar(position = position_dodge2(padding = 0.2), width = 0.8) +
  geom_text(stat = "count", aes(label = after_stat(count)), 
            position = position_dodge2(width = 0.8, padding = 0.2), vjust = -0.5) +
  scale_fill_brewer(palette = "Set2") +
  labs(
    title = "Count of Group Constellations after Preprocessing",
    x = "Trait Level",
    y = "Count"
  ) +
  facet_grid(. ~ Trait, scales = "free_x", space = "free_x") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1), 
    panel.grid.major.x = element_blank(),
    strip.text.x = element_text(face = "bold"),
    legend.position = "none", 
    plot.margin = margin(10, 30, 10, 10)  # Add small extra space
  ) +
  coord_cartesian(expand = TRUE) +
  theme(strip.text.x = element_text(size = 8, margin = margin(t = 5, b = 5))) + # Extra spacing for facet labels
  ylim(0, 155)


```



## Team Scores visualized 


```{r}
# boxplots of team score
ggplot(all_filtered_data, aes(x = Trait, y = team_score, fill = Trait)) +
  geom_boxplot(aes(group = interaction(Trait, Level))) +
  geom_hline(yintercept = 0, color = "red", size = 0.6) + 
  labs(
    title = "Boxplots of Team Scores across Group Constellations",
    x = "Personality Trait",
    y = "Team Score"
  ) +
  scale_fill_brewer(palette = "Set2") + # Custom trait colors
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none",
    axis.text = element_text(size = 10),
    plot.title = element_text(size = 14, face = "bold")
  ) +
  ylim(-0.3, 0.3)
```

```{r}
ggplot(summary_stats, aes(x = Level, y = mean_team_score, group = Trait, color = Trait)) +
  geom_point(size = 3) +  # Points for High and Low scores
  geom_line(size = 1) +   # Lines connecting the points
  geom_errorbar(aes(ymin = mean_team_score - se_team_score, ymax = mean_team_score + se_team_score), 
                width = 0.2) +  # Error bars for uncertainty
  labs(
    title = "Mean Team Scores with Standard Error",
    x = "Trait Level",
    y = "Mean Team Score",
    color = "Personality Trait"
  ) +
  theme_minimal() + 
  theme(
    axis.text = element_text(size = 10),
    plot.title = element_text(size = 14, face = "bold")
  )
```



## Visualizing Synergy Score

```{r}
# boxplots of synergy
ggplot(all_filtered_data, aes(x = Trait, y = synergy_score, fill = Trait)) +
  geom_boxplot(aes(group = interaction(Trait, Level))) +
  geom_hline(yintercept = 0, color = "red", size = 0.6) + 
  labs(
    title = "Boxplots of Synergy Scores across Group Constellations",
    x = "Personality Trait",
    y = "Synergy Score"
  ) +
  scale_fill_brewer(palette = "Set2") + # Custom trait colors
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none",
    axis.text = element_text(size = 10),
    plot.title = element_text(size = 14, face = "bold")
  ) +
  ylim(-0.3, 0.3)

```



```{r}
ggplot(summary_stats, aes(x = Level, y = mean_synergy_score, group = Trait, color = Trait)) +
  geom_point(size = 3) +  # Points for High and Low scores
  geom_line(size = 1) +   # Lines connecting the points
  geom_errorbar(aes(ymin = mean_synergy_score - se_synergy_score, ymax = mean_synergy_score + se_synergy_score), 
                width = 0.2) +  # Error bars for uncertainty
  labs(
    title = "Mean Synergy Scores with Standard Error",
    x = "Trait Level",
    y = "Mean Synergy Score",
    color = "Personality Trait"
  ) +
  theme_minimal() + 
  theme(
    axis.text = element_text(size = 10),
    plot.title = element_text(size = 14, face = "bold")
  )
```


## Turn-Takings visualized 

```{r}
# Calculate the overall mean of turn-takings
overall_mean <- mean(all_filtered_data$turn_takings, na.rm = TRUE)

# Create the plot
ggplot(all_filtered_data, aes(x = Trait, y = turn_takings, fill = Trait)) +
  geom_boxplot(aes(group = interaction(Trait, Level))) +
  geom_hline(yintercept = overall_mean, color = "red", size = 0.6) + 
  labs(
    title = "Boxplots of Turn-takings by Group Constellation",
    x = "Personality Trait",
    y = "Turn-takings"
  ) +
  scale_fill_brewer(palette = "Set2") + # Custom trait colors
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none",
    axis.text = element_text(size = 10),
    plot.title = element_text(size = 14, face = "bold")
  ) +
  ylim(0, 35)
```



```{r}
ggplot(summary_stats, aes(x = Level, y = mean_turntakings, group = Trait, color = Trait)) +
  geom_point(size = 3) +  # Points for High and Low scores
  geom_line(size = 1) +   # Lines connecting the points
  geom_errorbar(aes(ymin = mean_turntakings - se_turntakings, ymax = mean_turntakings + se_turntakings), 
                width = 0.2) +  # Error bars for uncertainty
  labs(
    title = "Mean Turn-takings with Standard Error",
    x = "Trait Level",
    y = "Mean Turn-takings",
    color = "Personality Trait"
  ) +
  theme_minimal() + 
  theme(
    axis.text = element_text(size = 10),
    plot.title = element_text(size = 14, face = "bold")
  )

```


